Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-01 paper_intersections.tex
Element intersection benchmark.

\subsection{Element Intersection Algorithms}
The first benchmark focuses on the 1d-3d and 2d-3d element intersections. We randomly generated
100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
In some of the empty cases, the bounding boxes did not collide, so the actual intersection algorithms were skipped. 
A single element pair was computed 100 times to obtain reasonable computational time.

@@

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
using \plucker coordinates, red values to \ngh code. The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
\notePE{Improve and complete...}

>>>>

\subsection{Element Intersection Algorithms}
The first benchmark focuses on the 1d-3d and 2d-3d element intersections. We randomly generated
100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
Only the pairs with non-colliding bounding boxes were included to the timing.  
Every element pair was computed 100 times to obtain reasonable computational time.
\noteJB{According to the results the time of single pair is on average 2e-5s. Normal system times have resolution about 20ms, hi-resolution timers
used in profiler have resolution about 1ms. So we need at least 10000 calls per single pair to get meaningful results.}

@@

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
using \plucker coordinates, red values to \ngh code. The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d. 
\noteJB{Just the opposite what we expect. Just by chance?}
